---
title: "Example analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(codeSimData)
library(ggplot2)
```

# Data preparation and setup
We first load in surface feature data, identify the feature centres, and load the flow fields.

```{r load_data}
# Dimples
dimplesField <- re1000weInf$dimples
dimples <- find.vortices.over.time(dimplesField)

# Scars
scarsField <- re1000weInf$scars
scars <- find.scars.over.time(scarsField)

# Surface divergence and vertical vorticity
surfDiv <- re1000weInf$surfDiv
vortZ <- re1000weInf$vortZ

# Integral scales
lengthscale <- re1000weInf$lengthscale # Pixels per integral length scale
timescale <- re1000weInf$timescale # Timestep per integral time scale
```


We select which snapshots to use, and which lags to use.
```{r select_times}
lags <- c(-1, 0, 1)
timesteps <- seq(from = 2, to = length(dimples) - max(lags), by = ceiling(timescale))
radii <- c(1:ceiling(lengthscale*3))

lx <- dim(surfDiv)[2]
ly <- dim(surfDiv)[3]
```

# Data analysis

We calculate the profile log likelihood for the global model:

```{r log_lik_global_model}
logLikGlobal.dimpDiv <- c(1:length(lags))
logLikGlobal.dimpVort <- c(1:length(lags))
logLikGlobal.scarDiv <- c(1:length(lags))
logLikGlobal.scarVort <- c(1:length(lags))
for (h_ind in 1:length(lags)) {
  # Log-likelihood for surface divergence
  res <- get.fit.specific.r.h(scars_list = scars, 
                              dimples_list = dimples, 
                              l_x = lx, 
                              l_y = ly, 
                              field = surfDiv, 
                              tidspunkt = timesteps, 
                              r = "infty", 
                              h = lags[h_ind], 
                              resType = "logLik")
  
  logLikGlobal.scarDiv[h_ind] <- res[1]
  logLikGlobal.dimpDiv[h_ind] <- res[2]
  
  # Log-likelihood for vertical vorticity
  res <- get.fit.specific.r.h(scars_list = scars, 
                              dimples_list = dimples, 
                              l_x = lx, 
                              l_y = ly, 
                              field = vortZ, 
                              tidspunkt = timesteps, 
                              r = "infty", 
                              h = lags[h_ind], 
                              resType = "logLik")
  logLikGlobal.scarVort[h_ind] <- res[1]
  logLikGlobal.dimpVort[h_ind] <- res[2]
}
rm(res)
```

We calculate the profile log likelihood for the local model:
```{r log_lik_local_model}
sDiv_log_lik <- make.logLik.matrix(scars_list = scars,
                   dimples_list = dimples,
                   l_x = lx,
                   l_y = ly,
                   field = surfDiv,
                   tidspunkt = timesteps,
                   radiar = radii,
                   lags = lags,
                   radiiForPrint = c(2, 5, 10, 20, 30, 40))

vortZ_log_lik <- make.logLik.matrix(scars_list = scars,
                   dimples_list = dimples,
                   l_x = lx,
                   l_y = ly,
                   field = vortZ,
                   tidspunkt = timesteps,
                   radiar = radii,
                   lags = lags,
                   radiiForPrint = c(2, 5, 10, 20, 30, 40))
```


# Results and plots
We compare the global and local models. Positive values here imply the local model outperforms the global model.
```{r glob_vs_loc}
print(paste("DimpDiv", max(sDiv_log_lik$dimples) - max(logLikGlobal.dimpDiv)))
print(paste("DimpVort", max(vortZ_log_lik$dimples) - max(logLikGlobal.dimpVort)))
print(paste("ScarDiv", max(sDiv_log_lik$scars) - max(logLikGlobal.scarDiv)))
print(paste("ScarVort", max(vortZ_log_lik$scars) - max(logLikGlobal.scarVort)))
```


We plot the resulting profile log likelihood for the local model.
```{r plot_data}
plot_data <- expand.grid(r = radii/lengthscale, tau = lags/timescale)
plot_data$dimpDiv <- array(t(sDiv_log_lik$dimples))
plot_data$scarDiv <- array(t(sDiv_log_lik$scars))
plot_data$dimpVort <- array(t(vortZ_log_lik$dimples))
plot_data$scarVort <- array(t(vortZ_log_lik$scars))

dimpDiv_plot <- ggplot(data = plot_data, mapping = aes(x = r, y = tau, fill = dimpDiv)) + geom_raster()
scarDiv_plot <- ggplot(data = plot_data, mapping = aes(x = r, y = tau, fill = scarDiv)) + geom_raster()
dimpVort_plot <- ggplot(data = plot_data, mapping = aes(x = r, y = tau, fill = dimpVort)) + geom_raster()
scarVort_plot <- ggplot(data = plot_data, mapping = aes(x = r, y = tau, fill = scarVort)) + geom_raster()
```

```{r dimpDiv_plot}
dimpDiv_plot
```

```{r scarDiv_plot}
scarDiv_plot
```

```{r dimpVort_plot}
dimpVort_plot
```

```{r scarVort_plot}
scarVort_plot
```
